Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Spaces and line widths
Grammar

\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Patrick Prosser \and Ciaran McCreesh\thanks{This work was supported by
the Engineering and Physical Sciences Research Council [grant number
EP/K503058/1]}\and Craig MacDonald \and Alice Miller}
\institute{University of Glasgow, Glasgow, Scotland \\ \email{patrick.prosser@glasgow.ac.uk}}
\authorrunning{Prosser, McCreesh, MacDonald, Miller}
\tocauthor{Patrick Prosser}
\maketitle

@@

\noindent
Note: criteria 10, 11 and 12 only apply when there are less boats than skippers

>>>>

\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Craig MacDonald \and Ciaran McCreesh \and Alice Miller \and Patrick Prosser}
\institute{University of Glasgow, Glasgow, Scotland \\ \email{patrick.prosser@glasgow.ac.uk}}
\authorrunning{MacDonald, McCreesh, Miller, Prosser}
\maketitle

@@

Note that criteria 10, 11 and 12 only apply when there are fewer boats than
skippers.
